%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Erfahrung}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {DevOps Engineer} % Job title
  {Dunamu Inc.} % Organization
  {Seoul, S.Korea} % Location
  {Sep. 2023 - Present} % Date(s)
  {
  }

  %---------------------------------------------------------
  \cventry
  {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
  {Danggeun Pay Inc. (KarrotPay)} % Organization
  {Seoul, S.Korea} % Location
  {Mar. 2021 - Jun. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Everything that matters.}
    \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
    \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)}
    \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.}
    \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
    \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.}
    \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
